%-------------------------
% Resume in Latex
% Author: Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingMY}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large BSc. Andrej Korman}} & Email: \href{mailto:andrejkorman@gmail.com}{andrejkorman@gmail.com}\\
  & Mobile: (+421) 910-463-863 \\
  & \href{https://github.com/Aj0SK}{github.com/Aj0SK} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Comenius University}{Bratislava, SK}
       {Master of Science in Computer Science} {June 2020 -- June 2022}
    \resumeSubheading
      {Comenius University}{Bratislava, SK}
      {Bachelor of Science in Computer Science; GPA:3.82}{Sept. 2017 -- June 2020}
      \resumeItemListStart
        \resumeItem{}
          {Relevant courses: Algorithms and Data Structures, System Programming, Database Programming, Programming in Java, Computer Networks, Mathematical Analysis, Algebra, Probability and Statistics, Cryptology.}
         \resumeItem{}
          {Thesis in DNA sequencing for bioinformatics applications. (Used Python, NumPy, SciPy)}
         \resumeItem{}
          {Teaching assistant of C++ course attended by more than 50 students (since Sept. 2019)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.innovatrics.com/}{Innovatrics}}{Bratislava, SK}
      {Junior Algorithm Developer}{March 2020 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Worked as a C++ developer on a biometric product. Developed testing metrics preventing software regressions between product versions. (Used C++, Python, Jira, Git)}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.sygic.com/about}{Sygic}}{Bratislava, SK}
      {C++ Junior Developer}{June 2019 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Worked as a C++ developer on a navigation product. Sped up incremental build time 5x by refactoring one of the biggest modules. (Used C++, Jenkins, Jira, Git)}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.eset.com/int/about/}{ESET}}{Bratislava, SK}
      {Junior Software Engineer}{June 2017 - Sept. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Worked as a C++ developer on a core module of ESET Endpoint Security and a translator module of ESET Smart Security. Replaced old faulty parser with a new, clean and tested. (Used C++, Python, Jira, Git)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Aj0SK/verilog}{Nand game CPU}}
      { Implemented a simple CPU design based on \href{http://nandgame.com/}{Nand game} in Verilog.}
    \resumeSubItem{\href{https://github.com/Aj0SK/my_os}{My-OS}}
      { Built a simple operating system for 32-bit architecture.}
    \resumeSubItem{\href{https://github.com/Aj0SK/lang_frontend}{lang\_frontend}}
      { Implemented an LLVM frontend using Flex and Bison for a simple language \href{https://llvm.org/docs/tutorial/MyFirstLanguageFrontend/}{Kaleidoscope}.}
    \resumeSubItem{\href{https://www.trojsten.sk/ls/}{Summer School of Programming}}
      { Prepared a two weeks long event for high school students. As a Lead Organizer, I prepared tasks, workshops and lectures for more than 100 students and coordinated a team of 15 organizers.}
%    \resumeSubItem{\href{https://www.ksp.sk/osp20/}{Online School of Programming}}
%      { Co-organized online event for general public during the COVID-19 pandemics. Prepared the introductory course into the Python programming.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Software}
      { (proficient): C++, Python, Git, Latex (familiar): C, Unix, C\#, Java, SQL, Rust, Assembly}
    \resumeSubItem{Languages}
      { English - fluent, French - beginner, Slovak - native}
  \resumeSubHeadingListEnd
  

\section{Volunteering}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.trojsten.sk/}{Trojsten}}{Slovakia, SK}
      {Lead Organizer}{Sept. 2015 - Present}
      \resumeItemListStart
        \resumeItem{}
          {An organizer of a year-long competition PRASK for primary school students. This includes preparation of algorithmic tasks as well as the organization of camps for best competitors.}
          \resumeItem{}
          {As a Lead organizer, I've been coordinating a team of 10 people since 2019.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
 \section{Honours and awards}
  \resumeSubHeadingListStart
    \resumeSubheadingMY
      {Annual Merit Scholarship}{2017, 2018, 2019}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {Received a scholarship awarded to TOP 5\% of students.}
      \resumeItemListEnd
    \resumeSubheadingMY
      {National selection camp for International Olympiad in Informatics}{2015}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {Placed among the top 10 participants of Slovak national olympiad in informatics.}
      \resumeItemListEnd
     \resumeSubheadingMY
      {2nd place at Slovak national programming competition ZENIT}{2017}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {Placed 2nd among more than 800 participants in a high school algorithmic competition.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
