%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingMY}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Andrej Korman}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{andrejkorman@gmail.com}\\
  \href{http://sourabhbajaj.com/}{} & Mobile : +421-910-463-863 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Comenius University}{Slovakia, SK}
      {Bachelor of Science in Computer Science;  GPA: 3.80}{Aug. 2017 -- Dec. 2020}
      \resumeItemListStart
        \resumeItem{}
          {Took many interesting courses including Algorithms and data structures, System programming, Database programming, Computer networks and also Mathematical analysis, Algebra etc. In my thesis I am now working on algorithm that will help bioinformatics during DNA sequencing.}
         \resumeItem{}
          {this year started as an assistent on C++ course}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sygic}{Bratislava, SK}
      {C++ Junior Developer}{June 2019 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Worked as a C++ developer on navigation product. Refactored one of the biggest modules and rapidly increased compilation time.(Used Jenkins, Jira, Git)}
      \resumeItemListEnd
      
    \resumeSubheading
      {ESET}{Bratislava, SK}
      {Junior Software Engineer}{June 2017 - Sept. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Worked as a C++ developer on a core module of ESET Endpoint Security as well as on a translator module of ESET Smart Security.(Used Python, Jira, Git)}
      \resumeItemListEnd

      \resumeSubheading
      {HighChem}{Bratislava, SK}
      {Software Engineer}{July 2016 - Aug. 2016}
      \resumeItemListStart
        \resumeItem{}
          {Developed various algorithms and heuristics in C\# for finding relations between molecules derived from their structure. This helps more than 2000 laboratories around the world to match new unknown chemicals with the ones in the database.(Used SVN)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Volunteering}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Trojsten}{Slovakia, SK}
      {Lead Organizer and Organizer}{Sept. 2015 -- Present}
      \resumeItemListStart
        \resumeItem{}
          {Organizer of a year long competition PRASK for primary school students. This includes preparation of algorithmic tasks as well as organization of camps for best competitors. For last year I am also the Lead organizer coordinating 10 other organizers.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
 \section{Honours and awards}
  \resumeSubHeadingListStart
    \resumeSubheadingMY
      {Annual Merit Scholarship}{Slovakia, SK}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {Received scholarship for less than 5\% of students with excellent results.}
      \resumeItemListEnd
    \resumeSubheadingMY
      {National selection camp for International Olympiad in Informatics}{Slovakia, SK}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {I placed in top 10 participants of our national olympiad in informatics.}
      \resumeItemListEnd
     \resumeSubheadingMY
      {2nd place at national programming competition ZENIT}{Slovakia, SK}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {Placed 2nd of around 900 participants.}
      \resumeItemListEnd 
      \resumeSubheadingMY
      {Poster at 66th Conference on Mass Spectrometry and Allied Topics}{}
      {}{}
      \resumeItemListStart
        \resumeItem{}
          {My work in HighChem was important part of presented work.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Summer School of Programming}
      { Two week event for high school students. As a Lead Organizer I had to prepare tasks, workshops and lectures for more than 100 high school students as well as coordinate team of 15 organizers.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Technologies}{: C++, C, C\#, Python, Java, Latex}
     \hfill
     \textbf{Other}{: data structures, problem solving}
   }
   \item{
    \textbf{Languages}{: English - upper-intermediate, Slovak - native}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
